Appendix 3: Estimating species interactions

### 2015-10-31 Harris_2015/manuscript-materials/draft.Rmd
closer

\setlength{\parindent}{1cm}

To the extent that nontrophic species interactions (such as competition) affect
community assembly, ecologists might expect to find signatures of these
interactions in species composition data [@macarthur_population_1958;
@diamond_island_1975]. Despite decades of work and several major controversies,
however [@lewin_santa_1983; @strong_ecological_1984; @connor_checkered_2013],
existing methods for detecting competition's effects on community structure are
unreliable [@gotelli_empirical_2009]. In particular, species' effects on one
another can become lost in the complex web of indirect effects. For example, the
competitive interaction between the two shrub species in Figure 1A can become
obscured by their shared tendency to occur in unshaded areas (Figure 1B). While
ecologists have long known that indirect effects can overwhelm direct ones at
the landscape level [@dodson_complementary_1970; @levine_competitive_1976], the
vast majority of our methods for drawing inferences from observational data do
not control for these effects [e.g. @diamond_island_1975;
@strong_ecological_1984; @gotelli_empirical_2009; @veech_probabilistic_2013;
@pollock_understanding_2014]. To the extent that indirect interactions like
those in Figure 1 are generally important [@dodson_complementary_1970], existing
methods will thus not provide much evidence regarding species interactions.

While competition doesn't reliably reduce co-occurrence rates at the
whole-landscape level (as most methods assume), it nevertheless does leave a
signal in the data (Figure 1C). For example, after partitioning the data set
into shaded sites and unshaded sites, there will be co-occurrence deficits in
each subset that might not be apparent at the whole-landscape level. More
generally, controlling for other species in the network will often be important
for obtaining reliable estimates of direct (conditional, or all-else-equal)
effects.  This kind of precision is difficult to obtain from null models, which
only simulate the most extreme possible scenario: that *all* direct and indirect
interactions are exactly zero. Nevertheless, null models have dominated this
field for more than three decades [@strong_ecological_1984;
@gotelli_empirical_2009].

Following @azaele_inferring_2010, this paper shows that Markov networks
[undirected graphical models also known as Markov random fields;
@murphy_machine_2012] can provide a framework for understanding the
landscape-level consequences of pairwise species interactions,
and for detecting them from observed presence-absence matrices. Markov networks
have been used in many scientific fields in similar contexts for decades, from
physics [where nearby particles interact magnetically; @cipra_introduction_1987]
to spatial statistics [where adjacent grid cells have correlated values;
@harris_contact_1974; @gelfand_modelling_2005]. While community ecologists
explored some related approaches in the 1980's [@whittam_species_1981],
they used severe approximations that led to unintelligible results
[e.g. "probabilities" greater than one; @gilpin_factors_1982].

Below, I introduce Markov networks and show how they can be used to simulate
landscape-level data from an interaction matrix or to make exact predictions
about the direct and indirect consequences of possible interaction matrices.
Then, using simulated data sets where the "true" interactions are known,
I compare this approach with several existing methods. Finally, I discuss
opportunities for extending the approach presented here to other problems in
community ecology, e.g. quantifying the overall effect of species interactions
on occurrence rates [@roughgarden_competition_1983] and disentangling the
effects of biotic versus abiotic interactions on species composition
[@pollock_understanding_2014].

@@

\raggedright
\setlength{\parindent}{1cm}

\noindent where the second sum is over all $\frac{1}{2}n(n-1)$ pairs of $n$ species. In this
model, $\alpha_{i}$ is an intercept term determining the amount that the presence
of species $i$ contributes to the log-probability of $\vec{y}$; it directly
controls the prevalence of species $i$. Similarly, $\beta_{ij}$ is the amount
that the co-occurrence of species $i$ and species $j$ contributes to the
log-probability; it controls the conditional relationship between two species,
i.e. the probability that they will be found together, after controlling for the
other species in the network (Figure 2A, Figure 2B). For example, $\beta_{ij}$
might have a value of $+2$ for two mutualists, indicating that the odds of
observing one species are $e^2$ times higher in sites where its partner is
present than in comparable sites where its partner is absent.

Because the relative probability of a presence-absence vector increases when
positively-associated species co-occur and decreases when negatively-associated
species co-occur, the model tends---all else equal---to produce assemblages that
have many pairs of positively-associated species and relatively few pairs of
negatively-associated species (exactly as an ecologist might expect).
Of course, if all else is *not* equal (e.g. Figure 1, where the presence of one
competitor is associated with release from another competitor), then species'
overall co-occurrence patterns can be more complicated, and may require summing
over the different possible assemblages (Figure 2B) to determine the overall
outcomes.

@@

\noindent \textbf{Evaluating model performance.}
For the simulated landscapes based on Figure 1, I assessed whether each method's
test statistic indicated a positive or negative relationship between the two
shrubs (Appendix 1). For the null model (Pairs), I calculated statistical
significance using its $Z$-score. For the Markov network, I used the Hessian
matrix to generate approximate confidence intervals and noted whether these
intervals included zero.

I then evaluated the relationship between each method's estimates and the "true"
interaction strengths among all of the species pairs from the larger simulated
landscapes. This determined which of the methods provide a consistent way to
know how strong species interactions are---regardless of which species were
present in a particular data set or how many observations were taken. To ensure
that the different test statistics (e.g. correlations versus $Z$ scores) were on
a common scale, I rescaled them using linear regression through the origin. After
rescaling each method’s estimates, I calculated squared errors between the scaled
interaction estimates and "true" interaction values across the simulated data
sets. These squared errors determined the proportion of variance explained
for different combinations of model type and landscape size (compared with a
null model that assumed all interaction strengths to be zero).

@@

\noindent
\textbf{Twenty species.}
Despite some variability across contexts (Figure 3), the four methods that
controlled for indirect effects (the Markov network, the generalized linear
models, and the two partial correlation-based methods) outperformed those
that did not.  Of these, the Markov network consistently performed the best,
especially on the smaller landscapes [which are also the most
representative of typical analyses in this field; @gotelli_empirical_2009].
As shown in Appendix [[X]], the standard errors associated with the estimates
in Figure 3 are all small (less than 0.01), so differences across methods should
not be attributed to sampling error.

Of the methods that did not control for indirect effects, Figure 3 shows that
simple correlation coefficients provided a more reliable indicator of species'
true interaction strengths than either the joint species distribution model
(BayesComm) or the null model (Pairs). The estimates from these
three approaches were tightly correlated (Figure 3B), suggesting that the
effect sizes from the null model (and, to a lesser extent, the correlation
matrices from joint species distribution models) only contain noisy versions of
the same information that could be obtained more easily and interpretably by
calculating correlation coefficients between species' presence-absence vectors.

Whereas Figure 3 summarizes the accuracy of each model's point estimates, Figure
4 compares the inferential value of the Markov network versus the null model.
When the "true" $\beta$ coefficient is near zero, the Markov network's 95%
confidence intervals usually include zero (but not quite 95% of the time), and
it is rare for the model to confidently attribute the wrong sign to a
coefficient (Figure 4A). The null model, by contrast, typically rejects the null
hypothesis at the $p=0.05$ level regardless of the underlying parameters, and
the sign of its $Z$-scores is not a reliable indicator of the interaction's
actual sign.

@@

The results presented above show that Markov networks can reliably recover
species' pairwise interactions from observational data, even for cases where
environmental heterogeneity and indirect interactions cause ecologists' typical
null modeling approaches to reliably fail. For cases where fitting a Markov
network is computationally infeasible, these results also indicate that partial
covariances and generalized linear models can both provide useful approximations.
The partial correlations' success on simulated data may not carry over to real
data sets, however; @loh_structure_2013 show that the linear approximations can
be less reliable in cases where the true interaction matrix contains more
structure (e.g. guilds or trophic levels). Similarly, the approximation involved
in using separate generalized linear models for each species can occasionally
lead to catastrophic overfitting with small-to-moderate sample sizes
[@lee_learning_2012]. For these reasons, it will usually be best to fit a Markov
network rather than one of the alternative methods when one’s computational
resources allow it.

It’s important to note that none of these methods can identify the exact nature
of the pairwise interactions [e.g. which species in a positively-associated
pair is facilitating the other; @schmidt_modeling_2012], particularly when real
pairs of species can reciprocally influence one another in multiple ways
simultaneously [@bruno_inclusion_2003]; with compositional data, there is only
enough information to provide a single number describing each species pair.
To estimate asymmetric interactions, such as commensalism or predation,
ecologists would need other kinds of data, as from time series, behavioral
observations, manipulative experiments, or natural history. These other sources
of information could also be used to augment the likelihood function with an
informative prior distribution, which could lead to better results on some real
data sets than was shown in Figure 3A.

Despite their limitations, Markov networks have enormous potential to improve
ecological understanding. In particular, they are less vulnerable than some
of the most commonly-used methods to mistakenly identifying positive species
interactions between competing species, and can make precise statements about
the conditions where indirect interactions will overwhelm direct ones. They also
provide a simple answer to the question of how competition should affect a
species' overall prevalence, which was a major flashpoint for the null model
debates in the 1980’s [@roughgarden_competition_1983; @strong_ecological_1984].
Equation 1 can be used to calculate the expected prevalence of a species in the
absence of biotic influences [$\frac{e^\alpha}{1 + e^{\alpha}}$; @lee_learning_2012].
Competition's effect on prevalence in a Markov network can then be calculated by
subtracting this value from the observed prevalence (cf Figure 2D). This kind of
insight would have been difficult to obtain without a generative model that
makes predictions about the consequences of species interactions; null models
(which presume *a priori* that interactions do not exist) have no way to make
such predictions.

Markov networks---particularly the Ising model for binary networks---have been
studied for nearly a century [@cipra_introduction_1987], and the models'
properties, capabilities, and limits are well-understood. Using the same
framework for species interactions would thus allow ecologists to tap into an
enormous set of existing discoveries and techniques for dealing with indirect
effects, stability, and alternative stable states. Numerous other extensions are
possible: for example, the states of the interaction network can be modeled as a
function of the local abiotic environment [@lee_learning_2012], which would
provide a rigorous and straightforward approach to the difficult and important
task of incorporating whole networks of biotic interactions into species
distribution models [@pollock_understanding_2014], leading to a
better understanding of the interplay between biotic and abiotic effects on
community structure. Alternatively, models could allow one species to affect the
interactions between two other species [@tjelmeland_markov_1998], tipping the
balance between facilitation and exploitation [@bruno_inclusion_2003].

Finally, the results presented here have important implications for
ecologists' continued use of null models for studying species interactions. Null
and neutral models can be useful for clarifying our thinking about the numerical
consequences of species' richness and abundance patterns
[@harris_occupancy_2011; @xiao_strong_2015], but deviations from a particular
null model must be interpreted with care [@roughgarden_competition_1983]. Even
in small networks with three species, it may simply not be possible to implicate
individual species pairs or specific ecological processes like competition by
rejecting a general-purpose null [@gotelli_empirical_2009], especially when the
test statistic is effectively just a correlation coefficient [[Figure 3B]].
When a non-null backdrop is not controlled for, Type I error rates can
skyrocket, the apparent sign of the interaction can change, and null models
can lead to reliably incorrect inferences (Figure 1, Figure 4).

@@

\noindent \textbf{Acknowledgements:}
This research was funded by a Graduate Research Fellowship from the US
National Science Foundation and benefited greatly from discussions with A.
Sih, M. L. Baskett, R. McElreath, R. J. Hijmans, A. C. Perry, and C. S. Tysor.
Additionally, A. K. Barner, E. Baldridge, E. P. White, D. Li, D. L. Miller, N.
Golding, N. J. Gotelli, C. F. Dormann, and two anonymous reviewers provided
very helpful feedback on the text.

@@

\noindent \textbf{Figure 2: A.} A small Markov network with two species, defined by its $\alpha$ and
$\beta$ values.  The abiotic environment favors the occurrence of each species
($\alpha >0$), particularly species 2 ($\alpha_2 > \alpha_1$). The negative
$\beta$ coefficient linking these two species implies that they co-occur less
than expected under independence. **B.** These coefficients determine the
probabilities of all four possible presence-absence combinations for Species 1
and Species 2. $\alpha_1$ is added to the exponent whenever Species 1 is present
($y_1 = 1$), but not when it is absent ($y_1 = 0$).  Similarly, the exponent
includes $\alpha_2$ only when species $2$ is present ($y_2 = 1$), and
$\beta$ only when both are present ($y_1y_2 = 1$). The normalizing constant $Z$,
ensures that the four probabilities sum to 1.  In this case, $Z$ is
about 18.5.  **C.** The expected frequencies of all possible
co-occurrence patterns between the two species of interest, as calculated in the
previous panel. **D.** If, as assumed in null model simulations, $\beta_{12}$
equaled zero (e.g. if the species no longer competed for the same resources),
then the reduction in competition would allow each species to increase its
overall occurrence rate.

\noindent \textbf{Figure 3: A.} Proportion of variance in interaction
coefficients explained by each method versus number of sampled locations.
**B.** The $Z$-scores produced by the null model ("Pairs") for each pair of
species can be predicted using the correlation between the presence-absence
vectors of those same species and from the number of sites on the landscape.

>>>>

\setlength{\parindent}{2em}

To the extent that nontrophic species interactions (such as competition) affect
community assembly, ecologists might expect to find signatures of these
interactions in species composition data [@macarthur_population_1958;
@diamond_island_1975]. Despite decades of work and several major controversies,
however [@lewin_santa_1983; @strong_ecological_1984; @connor_checkered_2013],
existing methods for detecting competition's effects on community structure are
unreliable [@gotelli_empirical_2009]. In particular, species' effects on one
another can become lost in a web of indirect effects. For example, the
competitive interaction between the two shrub species in Figure 1A is
obscured by their shared tendency to occur in unshaded areas (Figure 1B). While
ecologists have long known that indirect effects can overwhelm direct ones at
the landscape level [@dodson_complementary_1970; @levine_competitive_1976], the
vast majority of our methods for drawing inferences from observational data do
not control for these effects [e.g. @diamond_island_1975;
@strong_ecological_1984; @gotelli_empirical_2009; @veech_probabilistic_2013;
@pollock_understanding_2014]. To the extent that indirect interactions like
those in Figure 1 are generally important [@dodson_complementary_1970], existing
methods will not provide much evidence regarding species interactions.

While competition doesn't reliably reduce co-occurrence rates at the
whole-landscape level (as most methods assume), it nevertheless does leave a
signal in the data (Figure 1C). For example, after partitioning the data set
into shaded and unshaded sites, there will be co-occurrence deficits in
each subset that wouldn't otherwise be apparent. More generally, controlling for
other species in the network will often be important for obtaining reliable
estimates of direct (conditional, or all-else-equal) effects.  This kind of
precision is difficult to obtain from null models, which only simulate the most
extreme possible scenario: that *all* direct and indirect interactions are
exactly zero. Nevertheless, null models have dominated this field for more than
three decades [@strong_ecological_1984; @gotelli_empirical_2009].

Following @azaele_inferring_2010, this paper shows that Markov networks
[undirected graphical models also known as Markov random fields;
@murphy_machine_2012] can provide a framework for understanding the
landscape-level consequences of pairwise species interactions,
and for estimating them from observed presence-absence matrices. Markov networks
have been used in many scientific fields in similar contexts for decades, from
physics [where nearby particles interact magnetically; @cipra_introduction_1987]
to spatial statistics [where adjacent grid cells have correlated values;
@harris_contact_1974; @gelfand_modelling_2005]. While community ecologists
explored some related approaches in the 1980's [@whittam_species_1981],
they used severe approximations that led to unintelligible results
[e.g. "probabilities" greater than one; @gilpin_factors_1982].

Below, I demonstrate Markov networks' ability to produce exact predictions
about the direct and indirect consequences of an interaction matrix, and also to
make inferences about the species interactions that contributed to an observed
set of co-occurrences. Using simulated data sets where the "true" interactions
are known, I compare this approach with several existing methods. Finally, I
discuss opportunities for extending the approach presented here to other
problems in community ecology, e.g. quantifying the overall effect of species
interactions on occurrence rates [@roughgarden_competition_1983] and
disentangling the effects of biotic versus abiotic interactions on species
composition [@pollock_understanding_2014].

@@

\raggedright
\setlength{\parindent}{2em}

\noindent where the second sum is over all $\frac{1}{2}n(n-1)$ pairs of $n$
species. In this model, $\alpha_{i}$ is an intercept term determining the amount
that the presence of species $i$ contributes to the log-probability of
$\vec{y}$; it directly controls the prevalence of species $i$. Similarly,
$\beta_{ij}$ is the amount that the co-occurrence of species $i$ and species $j$
contributes to the log-probability; it controls the conditional relationship
between two species, i.e. the probability that they will be found together,
after controlling for the other species in the network (Figure 2A, Figure 2B).
For example, if $\beta_{ij} = -2$, then each species' odds of occurrence are
$exp{2}$ times lower when the other one is present (as compared with otherwise
comparable sites). Because the relative probability of a presence-absence vector
increases when positively-associated species co-occur and decreases when
negatively-associated species co-occur, the model tends---all else equal---to
produce assemblages that have many pairs of positively-associated species and
relatively few pairs of negatively-associated species (exactly as an ecologist
might expect). Of course, if all else is *not* equal (e.g. Figure 1, where the
presence of one competitor is associated with release from another competitor),
then species' overall co-occurrence patterns can be more complicated, and may
require summing over the different possible assemblages (Figure 2B) to determine
the overall outcomes.

@@

\noindent \textbf{Evaluating model performance.}
For the simulated landscapes based on Figure 1, I assessed whether each method's
test statistic indicated a positive or negative relationship between the two
shrubs (Appendix 1). For the null model (Pairs), I calculated statistical
significance using its $Z$-score. For the Markov network, I used the Hessian
matrix to generate approximate confidence intervals.

I then evaluated the relationship between each method's estimates and the "true"
interaction strengths among all of the species pairs from the larger simulated
landscapes. This determined which of the methods provide a consistent way to
know how strong species interactions are---regardless of which species were
present in a particular data set or how many observations were taken. To ensure
that the different test statistics (e.g. correlations versus $Z$ scores) were on
a common scale, I rescaled them using linear regression through the origin. I
then calculated the proportion of variance explained for different combinations
of model type and landscape size (compared with a null model that assumed all
interaction strengths to be zero).

@@

\noindent
\textbf{Twenty species.}
Despite some variability across contexts (Figure 3), the four methods that
controlled for indirect effects (the Markov network, the generalized linear
models, and the two partial correlation-based methods) outperformed those
that did not.  Of these, the Markov network consistently performed the best,
especially on the smaller landscapes [which are also the most
representative of typical analyses in this field; @gotelli_empirical_2009].
As shown in Appendix [[X]], the standard errors associated with the estimates
in Figure 3 are small (less than 0.01), so these differences should not be
attributed to sampling error.

Of the methods that did not control for indirect effects, Figure 3 shows that
simple correlation coefficients provided a more reliable indicator of species'
true interaction strengths than either the joint species distribution model
(BayesComm) or the null model (Pairs). The estimates from these
three approaches were tightly correlated (Figure [[3B]]), suggesting that the
null model only contains a noisy version of the same information that could be
obtained more easily and interpretably with simple correlation coefficients.

Finally, we can evaluate the models' statistical inferences.  Figure 4 shows,
across a range of true interaction strengths, the probability that the null model
or the Markov network will predict the wrong sign of the interaction with 95%
confidence.  The null model makes such errors nearly 8 times as often as the
Markov network, even though it only reject the null hypothesis twice as often
overall [[Appendix]].  The Markov network's errors were also more concentrated
around 0, so it never misclassified strong interactions like the null model did.

@@

The results presented above show that Markov networks can reliably recover
species' pairwise interactions from observational data, even for cases where
environmental heterogeneity and indirect interactions cause ecologists' typical
null modeling approaches to reliably fail. Partial covariances and generalized
linear models can both provide computationally efficient approximations, but
with somewhat lower accuracy. The difference in accuracy may be larger for real
data sets than for the simulated landscapes in Figure 3, however; linear
approximations to the Markov network make larger errors when the interaction
matrix is structured [e.g. due to guilds or trophic levels;
@loh_structure_2013]. Similarly, the separate generalized linear models
for each species can severely overfit in some cases [@lee_learning_2012]. The
full Markov network should thus be preferred to the approximations when
it is computationally feasible.

Compositional data only has enough degrees of freedom to estimate one interaction
per species pair [@schmidt_modeling_2012], so none of these methods can identify
the exact nature of the pairwise interactions [e.g. which species in a
positively-associated pair is facilitating the other]. To estimate asymmetric
interactions, such as commensalism or predation, ecologists could use time
series, behavioral observations, manipulative experiments, or natural history.
These other sources of information could also be used to augment the likelihood
function with an informative prior distribution, reducing ecologists' eror and
uncertainty.

Despite their limitations, Markov networks have enormous potential to improve
ecological understanding. In particular, they are less vulnerable than some
of the most commonly-used methods to mistakenly identifying positive species
interactions between competing species, and can make precise statements about
the conditions where indirect interactions will overwhelm direct ones. They also
provide a simple answer to the question of how competition should affect a
species' overall prevalence, which was a major flashpoint for the null model
debates in the 1980’s [@roughgarden_competition_1983; @strong_ecological_1984].
Equation 1 can be used to calculate the expected prevalence of a species in the
absence of biotic influences [$\frac{e^\alpha}{1 + e^{\alpha}}$; @lee_learning_2012].
Competition's effect on prevalence in a Markov network can then be calculated by
subtracting this value from the observed prevalence (cf Figure 2D). This kind of
insight would have been difficult to obtain without a generative model that
predicts the consequences of species interactions (as opposed to null
simulations that omit interactions entirely).

Markov networks---particularly the Ising model for binary networks---have been
studied for nearly a century [@cipra_introduction_1987], and the models are
well-understood. Using the same framework for species interactions would thus
allow ecologists to tap into a vast set of existing discoveries and techniques
for dealing with indirect effects, stability, and alternative stable states.
Numerous other extensions are possible: for example, the states of the
interaction network can be modeled as a function of the local abiotic
environment [@lee_learning_2012], which would help incorporate networks of
biotic interactions into species distribution models
[@pollock_understanding_2014] and lead to a better understanding of the
interplay between biotic and abiotic effects on community structure.
Alternatively, models could allow one species to alter the relationship between
two other species [@tjelmeland_markov_1998; cf @bruno_inclusion_2003].

Finally, the results presented here have important implications for
ecologists' continued use of null models for studying species interactions. Null
and neutral models can be useful for clarifying our thinking
[@harris_occupancy_2011; @xiao_strong_2015], but deviations from a particular
null model must be interpreted with care [@roughgarden_competition_1983]. Even
in small networks with three species, it may simply not be possible to implicate
specific ecological processes like competition by rejecting a general-purpose
null [@gotelli_empirical_2009], especially when the test statistic is
effectively just a correlation coefficient [[Figure 3B]]. When a non-null
backdrop is not controlled for, Type I error rates can skyrocket, the apparent
sign of the interaction can change, and null models can lead to reliably
incorrect inferences (Figure 1, Figure 4).

@@

\noindent \textbf{Acknowledgements:}
This work benefited greatly from discussions with A. Sih, M. L. Baskett, R.
McElreath, R. J. Hijmans, A. C. Perry, and C. S. Tysor. Additionally, A. K.
Barner, E. Baldridge, E. P. White, D. Li, D. L. Miller, N. Golding, N. J.
Gotelli, C. F. Dormann, and two anonymous reviewers provided very helpful
feedback on the text. This research was partially supported by a Graduate
Research Fellowship from the US National Science Foundation and by the Gordon
and Betty Moore Foundation's Data-Driven Discovery Initiative through Grant
GBMF4563 to E. P. White.

@@

\noindent \textbf{Figure 2: A.} A small Markov network, defined by its $\alpha$ and
$\beta$ values.  The abiotic environment favors the occurrence of each species
($\alpha >0$), particularly species 2 ($\alpha_2 > \alpha_1$). The negative
$\beta_12$ coefficient is consistent with competition between the two species.
**B.** The coefficients determine the probabilities of all four possible
presence-absence combinations for Species 1 and Species 2. $\alpha_1$ is added
to the exponent whenever Species 1 is present ($y_1 = 1$), but not when it is
absent ($y_1 = 0$).  Similarly, the exponent includes $\alpha_2$ only when
species $2$ is present ($y_2 = 1$), and includes $\beta_12$ only when both are
present ($y_1y_2 = 1$). The normalizing constant $Z$, ensures that the four
probabilities sum to 1.  In this case, $Z$ is about 18.5.  **C.** The expected
frequencies of all possible co-occurrence patterns between the two species of
interest, as calculated in the previous panel. **D.** If $\beta_{12}$ equaled
zero (e.g. if the species no longer competed for the same resources), then the
each species' overall occurrence rates would increase.

\noindent \textbf{Figure 3:} Proportion of variance in interaction
coefficients explained by each method versus number of sampled locations.
